---
title: "Visualizations of Laptop Specs in March 2022"
author: "Arthur Jordan"
date: '2022-04-06'
output: html_document
---

```{r setup, include=FALSE}

library(GGally)
library(ggthemes)
library(knitr)
library(RColorBrewer)
library(scales)
library(tidytext)
library(tidyverse)
opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Laptop Specs
# Inspecting laptop data

The data is based on the 'Laptop Specs and latest price' from Kaggle: https://www.kaggle.com/datasets/kuchhbhi/latest-laptop-price-list,
which was originally scraped from flipkart.com using an automated chrome web extension tool called Instant Data Scrapper. When we glimpse the data, we discover the following:

23 total columns: 

brand, model, processor_brand, processor_name, processor_gnrtn, ram_gb, ram_type, ssd, hdd, os, os_bit, graphics_card_gb, 

weight, display_size, warranty, Touchscreen, msoffice, latest_price, old_price, discount, star_rating, ratings, reviews


Column Types:

chr - brand, model, processor_brand, processor_name, processor_gnrtn, ram_gb, ram_type, ssd, hdd, os, os_bit, weigth, display_size, Touchscreen, msoffice

dbl - graphics_card_gb, warranty, latest_price, old_price, discount, star_rating, ratings, reviews



```{r}
laptop_data <- read_csv("data/Cleaned_Laptop_data.csv")
glimpse(laptop_data)
```

# Number of observations per brand 

```{r}
laptop_data %>%
  count(processor_name, sort = TRUE) %>%
  kable(caption = "Number of Processors per Processor Brand")
```

# Barcharts that visualize various laptop metrics

```{r}

laptop_data %>%
  group_by(brand) %>%
  summarize(count = n()) %>%
  mutate(brand = fct_reorder(brand, count)) %>%
  ggplot(aes(y = brand,
             x = count)) +
  geom_col() +
  scale_fill_colorblind(name = "Processor Brand") +
  labs(title = "Distribution of Laptop Brands in March 2022",
       x = "Total Number of laptops",
       y = "Laptop Brand") +
  theme()
  
  
laptop_data %>%
  group_by(processor_brand) %>%
  summarize(count = n()) %>%
  mutate(processor_brand = fct_reorder(processor_brand, count)) %>%
  ggplot(aes(y = processor_brand,
             x = count,
             fill = processor_brand)) +
  geom_col() +
  scale_x_continuous() +
  scale_fill_colorblind(name = "Processor Brand") +
  labs(title = "Distribution of Processor Brands in March 2022",
       x = "Total Number of processors",
       y = "Processor Brand") +
  theme()

colored_laptop_data <- laptop_data %>%
  group_by(brand) %>%
  mutate(new_price = latest_price / 1000) %>%
  mutate(brand = fct_reorder(brand, new_price, .desc = FALSE)) %>%
  ggplot(aes(x = new_price,
             y = brand,
             fill = brand)) +
  geom_col(position = "identity") +
  theme_minimal() +
  scale_x_continuous(labels=scales::dollar_format()) +
  labs(title = "Laptop Prices across Laptop Brands",
       x = "Laptop Price",
       y = "Laptop Brand",
       caption = "The data is based on the 'Laptop Specs and latest price' from Kaggle: https://www.kaggle.com/datasets/kuchhbhi/latest-laptop-price-list")

colored_laptop_data


```

# Density Plots that visualize various laptop metrics
```{r}
# Density plot 1: Star Rating Density among Processor Brands by Operating System
colored_laptop_data <- laptop_data %>%
  mutate(processor_brand = fct_reorder(processor_brand, star_rating)) %>%
  ggplot(aes(x = star_rating,
             fill = processor_brand)) +
  geom_density(alpha = .5) +
  facet_wrap(~os) +
  scale_fill_colorblind()

colored_laptop_data

# Density plot 2: Star Rating Density among Ram Types by Operating System
colored_laptop_data <- laptop_data %>%
  mutate(ram_type = fct_reorder(ram_type, star_rating)) %>%
  ggplot(aes(x = star_rating,
             fill = ram_type)) +
  geom_density(alpha = .5) +
  facet_wrap(~ram_gb) +
  scale_fill_colorblind() +
  labs(title = "Star Rating Distribution across RAM Types",
       subtitle = "  grouped by RAM size",
       x = "Star_Rating",
       caption = "The data is based on the 'Laptop Specs and latest price' from Kaggle: https://www.kaggle.com/datasets/kuchhbhi/latest-laptop-price-list")

colored_laptop_data
```




```{r}
laptop_data %>%
  mutate(new_price = latest_price / 1000) %>%
  ggplot(aes(x = processor_brand,
             y = new_price,
             fill = fct_reorder(processor_brand, new_price, .desc = TRUE))) +
  geom_boxplot() +
  scale_y_continuous(name = "Laptop Price ($)", labels = scales::label_dollar()) +
  scale_fill_colorblind() +
  guides(fill=guide_legend(title="Processor Brand")) +
  labs(title = "Distribution of Laptop Prices across Processor Brands",
       x = "Processor Brand",
       caption = "The data is based on the 'Laptop Specs and latest price' from Kaggle: https://www.kaggle.com/datasets/kuchhbhi/latest-laptop-price-list")
  
```







