---
title: "laptop_visualizations"
author: "Arthur Jordan"
date: '2022-04-06'
output: html_document
---

```{r setup, include=FALSE}

library(GGally)
library(ggthemes)
library(knitr)
library(RColorBrewer)
library(tidytext)
library(tidyverse)
opts_chunk$set(echo = TRUE)
```

## Laptop Specs
# Inspecting laptop data

The data is based on the 'Laptop Specs and latest price' from Kaggle: https://www.kaggle.com/datasets/kuchhbhi/latest-laptop-price-list,
which was originally scraped from flipkart.com using an automated chrome web extension tool called Instant Data Scrapper. When we glimpse the data, we discover the following:

23 total columns: 

brand, model, processor_brand, processor_name, processor_gnrtn, ram_gb, ram_type, ssd, hdd, os, os_bit, graphics_card_gb, 

weight, display_size, warranty, Touchscreen, msoffice, latest_price, old_price, discount, star_rating, ratings, reviews


Column Types:

chr - brand, model, processor_brand, processor_name, processor_gnrtn, ram_gb, ram_type, ssd, hdd, os, os_bit, weigth, display_size, Touchscreen, msoffice

dbl - graphics_card_gb, warranty, latest_price, old_price, discount, star_rating, ratings, reviews



```{r}
laptop_data <- read_csv("data/Cleaned_Laptop_data.csv")
glimpse(laptop_data)
```

# Number of observations per brand 

```{r}
laptop_data %>%
  count(processor_brand, sort = TRUE) %>%
  kable(caption = "Number of observations per processor_brand")
```

# Barchart of total number of laptops per laptop brand

```{r}

laptop_data %>%
  group_by(brand) %>%
  summarize(count = n()) %>%
  mutate(brand = fct_reorder(brand, count)) %>%
  ggplot(aes(y = brand,
             x = count)) +
  geom_col() +
  scale_fill_colorblind(name = "Processor Brand") +
  labs(title = "Distribution of Laptop Brands in March 2022",
       x = "Total Number of laptops",
       y = "Laptop Brand") +
  theme()
  
  
laptop_data %>%
  group_by(brand, processor_brand) %>%
  summarize(count = n()) %>%
  mutate(brand = fct_reorder(brand, count)) %>%
  ggplot(aes(y = brand,
             x = count,
             fill = processor_brand)) +
  geom_col() +
  scale_fill_colorblind(name = "Processor Brand") +
  labs(title = "Total Number of Laptops per Laptop Brand in March 2022",
       x = "Total Number of laptops",
       y = "Laptop Brand") +
  theme()
```

```{r}
colored_laptop_data <- laptop_data %>%
  group_by(brand, ram_type) %>%
  ggplot(aes(y = brand,
             fill = ram_type)) +
  geom_bar(position = "fill") +
  theme_minimal()

colored_laptop_data + scale_fill_brewer(palette = "Spectral")
  
```


```{r}
laptop_data %>%
  ggplot(aes(x = star_rating,
             fill = processor_brand)) +
  geom_density(alpha = .5) +
  facet_wrap(~ram_type)
  
```



# Stacked bars of process_brand
```{r}
 laptop_data %>%
  ggplot(aes(y = processor_brand,
            fill = processor_name)) +
  geom_bar(position = "fill") +
  scale_fill_colorblind() +
  labs(y = "Processor Brand") +
  scale_fill_discrete(name = "Processor Name")
```

# Visualizing distribution of categorical variable - brand
```{r}
laptop_data %>%
  group_by(brand, model) %>%
  ggplot(aes(y = brand,
             fill = processor_brand)) +
  geom_bar() +
  scale_fill_colorblind()
```


```{r}

laptop_data %>%
  group_by(processor_name, latest_price) %>%
  summarize(latest_price = latest_price / 100) %>%
  ggplot(aes(x = latest_price,
             y = processor_name)) +
  geom_col()
```







